Impact of switching bug trackers: a case study on a medium-sized open source project

### 2019-04-07 article/article.tex
Snapshot (Jupyter notebook works fine).

\begin{document}
%
\title{Impact of switching bug trackers: a case study on a medium-sized open source project}
%
\author{Th\'eo Zimmermann\\
$\Pi R^2$, Inria and
IRIF, Paris-Diderot University\\
Paris, France\\
Email: theo@irif.fr
\and
Annal\'i Casanueva Art\'is\thanks{This work was partly funded by El Conacyt of the Mexican government.}\\
Paris School of Economics\\
Paris, France}
%
\maketitle
%
\begin{abstract}
For most software projects, the bug tracker is an essential tool. In open source development, this tool plays an even more central role as it is generally open to all users, who are encouraged to test the software and report bugs. Previous studies have highlighted the act of reporting a bug as a first step leading a user to become an active contributor.

@@

In this paper, we study the case of the Coq proof assistant, a medium-sized open source software project. We use the switch, from Bugzilla to GitHub, of the project's bug tracker, to analyze how a change in the bug reporting environment affects the number of bugs, reporters, bug comments and commentators. Using a Regression on Discontinuity design (RDD)~\cite{angrist2008mostly,angrist2014mastering,jacob2012practical,lee2010regression}, we find strong evidence that the change of platform increased the number of bug reports and comments by developers, and increased the number of distinct commentators each week among non-developers. Our results suggest that switching from Bugzilla to GitHub made the bug reporting process easier and more appealing but also opened the software development to more external contributors and stimulated discussion around bugs (notably between developers and non-developers).

@@

The rest of this paper is organized as follows: In Sec.~\ref{related-work}, we discuss related work. In Sec.~\ref{context}, we present the Coq project and the context of the switch. In Sec.~\ref{hypotheses}, we formulate hypotheses on the impact of the switch. In Sec.~\ref{migration}, we explain the migration process. In Sec.~\ref{data}, we describe the data collection and pre-processing method, and we list the variables of interest. In Sec.~\ref{descriptive-stats}, we give a preliminary view of the bug tracking activity. In Sec.~\ref{methodology}, we explain the Regression on Discontinuity methodology, of which we present the results in Sec.~\ref{results}. We interpret the results and relate them to our hypotheses in Sec.~\ref{discussion}. We discuss the threats to validity and  present robustness checks in Sec.~\ref{threats}. We conclude in Sec.~\ref{conclusion}.

@@

From 2007 to 2017, the Coq bug tracker platform was a self-hosted Bugzilla instance (before this, from 2001 to 2007 it was using JitterBug, a now discontinued bug tracking system, and before 2001 a simple mailing list). In 2017, developers had become quite accustomed to the look and feel of discussion threads on GitHub pull requests, which offered an arguably nicer experience than the Bugzilla bug tracker. Younger developers were frustrated by what they perceived as an older and heavier platform. The rest of the developers were convinced to migrate towards a non-self-hosted solution in August 2017, when the whole Coq website was shut down for more than a week  because an IT team was frightened by a scam bug report.\footnote{\url{https://sympa.inria.fr/sympa/arc/coq-club/2017-08/msg00040.html}}

The expected advantages of the GitHub issue tracker over Bugzilla were:
\begin{itemize}
\item Better formatting, ability to edit comments, and more generally a more pleasant tool to use. According to some Coq developers, Bugzilla was unpleasant enough to discourage developers to use it to its full potential.
\item Version control integration: Browsing between code, pull requests and bug reports is easier when everything is in the same place. Furthermore, it means a common notification, mention, and assignment system.
\item Better indexing by search engines.
\item Shared management of permissions, milestones, categories (labels), etc.
\item Easier to get started for newcomers (especially as many may already know GitHub and already have a GitHub account).
\end{itemize}

The possible drawbacks were mostly that GitHub provides a less advanced system with very few customization options. In particular:
\begin{itemize}
\item The permission system is much less fine-grained. Giving triaging rights to users requires giving them ``write access'', which includes commit rights on non-protected branches. That's why the Coq GitHub repository now only has protected branches (and accidentally-pushed topic branches are promptly deleted).
\item Creating a new bug report does not require filling a form, but typing a message. Fortunately, issue templates help give some hints towards the expected structure of the report, and being able to strip this template can actually give flexibility to developers who might open new issues for concerns that do not qualify as bugs.
\item There is no import mechanism that allows to keep the number and author of preexisting reports. Fortunately, as we will see in Sec.~\ref{migration}, it was still possible to import bug reports while keeping most of the meta-information and renumbering the fewest possible bug reports. This was an important requirement for the switch.
\end{itemize}

\section{Hypotheses}

\label{hypotheses}
%ambre: I think this section should be expanded a bit to add motivation for the hypotheses

Given the advantages of the GitHub issue tracker that were listed above, one could expect the switch to:
\begin{description}
\item[H1] Increase the bug tracking activity, in terms of the number of reported bugs;
\item[H2] Extend the pool of bug reporters and commentators;
\item[H3] Increase the bug tracking activity, in terms of the amount of interaction between users and developers.
\end{description}

@@

All the data for this study was extracted on January 17\textsuperscript{th}, 2019 using the GitHub GraphQL API \cite{github_graphql_API}. Using this API allows to do large requests (100 nodes in a single request) with just the information we need (thus both reducing the bandwidth usage and speeding up the extraction process). We provide the extracted data as CSV files and a Jupyter notebook\footnote{\url{https://github.com/Zimmi48/impact-of-switching-bug-trackers}.} with the code to request this data from GitHub, to load the CSV files, to run the pre-processing steps, and the analyses.%, and the robustness checks.

@@

\paragraph{Excluding specific reporters}
We have one specific reporter, Jason Gross, who is alone responsible for almost a quarter of all bug reports. To avoid having the behavior of a single individual strongly impact the overall statistics, we exclude his comments, bug reports and the comments they received from our analysis. Similarly, we also exclude the developer who was the main advocate of the bug tracker switch as it could have influenced his behavior before and after the switch.

@@

The companion Jupyter notebook contains an extensive array of descriptive tables and figures, such as the distribution of bug reporting in the year and in the day, graphs of bug reporting for individual developers, etc. We only present a subset of these results.

@@

\subsection{Influence of new releases}
\label{influence_release}

\paragraph{Influence on the number of bug reports}
We expect release dates to be correlated to peaks of activity on the bug tracker, in particular peaks of new bug reports. Indeed, users will generally test new releases, for instance by trying to port preexisting projects to the new version, which might lead them to find new bugs (either regressions or bugs related to new features). In Fig.~\ref{bug_nb_with_releases}, we can see that while release dates are generally correlated to peaks of new bug reports by non-developers, this is not so much the case of reports by developers. We can also notice that beta releases are often correlated to higher peaks than final releases which is not surprising given that the users who test beta versions are more likely to be ready to report bugs, and beta versions are likely to be less polished.

The highest peak is in 2015, after the first beta release of version 8.5. This was the first release in more than two years and it contained five big new features (``the result of five specific long-term projects''\footnote{Quote from:\\ \url{https://coq.inria.fr/distrib/V8.9.0/refman/credits.html\#credits-version-8-5}\\
The next quotes are coming from the following sections of the same chapter of the Coq reference manual.}). Stabilizing these features and their (unplanned) interactions required more than a year of testing and three beta releases. The 8.5 release was both hard on developers, who found the release cycle too long, and on users, who were impacted by many compatibility issues. Consequently, a different approach was taken for the following releases: versions 8.6, 8.7 and 8.8 were ``developed on a time-based development cycle'' and contain ``the result of refinements, stabilization of features and cleanups of the internals of the system along with a few new features''. Attention was given to regression testing: changes were systematically tested by building a selection of the largest Coq projects. Therefore, it is not surprising that these frequent releases are correlated to smaller peaks of new bug reports.

%IMPORTANT: metre une phrase dans la partie description des variables qui indique qu'on fait 4 semaines pour celui la.
\begin{figure}
\includegraphics{bug_nb_with_releases.eps}
\caption{Number of bug reports by 4-week period with release dates (since 2008).} \label{bug_nb_with_releases}
\end{figure}

\paragraph{Influence on the number of comments}
In Fig.~\ref{comments_with_releases}, we can see that release dates are correlated to peaks of comments by developers (and not so much by other people). This is explained by the fact that bug reports are generally answered by developers, thus any peak in bug reporting is bound to induce a peak in bug commenting by developers.

\begin{figure}
\includegraphics{comments_with_releases.eps}
\caption{Number of bug comments by 4-week period with release dates (since 2008).} \label{comments_with_releases}
\end{figure}

\begin{figure}
\includegraphics{reporters_with_releases.eps}
\caption{Average number of weekly distinct reporters by 4-week period with release dates (since 2008).} \label{reporters_with_releases}
\end{figure}

\begin{figure}
\includegraphics{commentators_with_releases.eps}
\caption{Average number of weekly distinct commentators by 4-week period with release dates (since 2008).} \label{commentators_with_releases}
\end{figure}

@@

We exploit the fact that the switch from Bugzilla to GitHub can be seen as a clear cutoff in time to use a temporal sharp Regression in Discontinuity design (RDD) to estimate the effects of the switch on our outcome variables; to determine if these estimated effects are statistically significant; and to interpret these effects in a causal way. 
The idea behind RDD is that factors that influence bug reporting activity are fairly similar just before and just after the cut-off point, which makes the changes observed between just after and just before the cut-off a consequence of the change that occurred at the cut-off (i.e., the switch of bug reporting platform).

@@

@@

\begin{table}
\centering
\caption{Estimated impact of the switch on the number of bugs. Coefficients are highlighted if they are statistically significant with $p<0.1$ ($\dagger$), $p<0.05$ (*), $p<0.01$ (**) or $p<0.001$ (***). Standard error is in parentheses.}
\label{tab:bug_nb}
\input{bug_nb_rd.tex}
\end{table}

\begin{figure}
\includegraphics{bug_nb_rd.png}
\caption{Average number of bug reports per day before and after the migration (with fitting lines and confidence intervals from the regression results).} \label{bug_nb_rd}
\end{figure}

@@

\begin{figure}
\includegraphics{reporter_nb_rd.png}
\caption{Average number of distinct reporters each week before and after the migration (with fitting lines and confidence intervals from the regression results).} \label{reporter_nb_rd}
\end{figure}

@@

\begin{figure}
\includegraphics{comment_nb_rd.png}
\caption{Average number of bug comments per day before and after the migration (with fitting lines and confidence intervals from the regression results).} \label{comment_nb_rd}
\end{figure}

@@

\begin{figure}
\includegraphics{commentator_nb_rd.png}
\caption{Average number of distinct commentators each week before and after the switch (with fitting lines and confidence intervals from the regression results).} \label{commentator_nb_rd}
\end{figure}

@@

The biggest concern that we have in our analysis is the fact that the date of the switch is close to the release of a new version of Coq. The release of version 8.7.0 took place on October 17\textsuperscript{th}, and the migration on October 18\textsuperscript{th}. Then, the hypothesis that there is no other discontinuity around the threshold of interest does not completely hold in our case.
%First, we can argue that only our result on the number of comments by developers is threatened: the other statistically significant effects that we observed are not threatened because there is usually no peak in the corresponding variables after new releases.
%Second, we can also argue that there should have been a similar (or higher) peak in the month before the switch since the first beta of 8.7 had been released then (and beta releases generally result in higher peaks).
To confirm that this is not what is driving our results, we conduct two robustness checks with our data. The first consists in removing the two weeks following the 8.7.0 release (and the switch) from our Regressions in Discontinuity. With these periods removed, the regressions still give very close results. The second consists in including a binary control variable that is equal to one if the period is in the two weeks after a release and zero otherwise. This control variable will capture the high peaks due to the release without the need of eliminating periods close to the switch. Again, our results remain very similar when we include this control variable.

@@

@@

%We also conduct one standard robustness check for Regression in Discontinuity analysis by changing the time window of the analysis to fifteen and to ten periods before and after the switch. Our main results are robust to these changes.

\subsection{External validity}

@@

% When to switch? It would be useful to come up with measures that indicate when a bug tracker is not adapted and a switch to another platform would be an improvement. (Or depending on specific objectives.)

\scriptsize
%\paragraph{}
\noindent \footnotesize{\textbf{Supporting data.}}
We provide our extraction and analysis code as a Jupyter notebook and the data we used as CSV files. We also provide the XML export of Bugzilla that was used for the migration and the migration script. Everything is available from \url{https://github.com/Zimmi48/impact-of-switching-bug-trackers}.
%\paragraph{}

@@

\noindent\footnotesize{\textbf{Acknowledgements.}}
We would like to thank Ambre Williams for valuable advice and help on the design and implementation of the data analyses and C\'ecile Rottner for general advice, support, and proof-reading.
We would like to thank Andriy Berestovskyy for providing the Bugzilla import tool, and Martin Michlmayr for doing the first steps in porting our modifications upstream.

>>>>

\begin{document}
%
\title{Impact of switching bug trackers: a case study on a medium-sized open source project}
%
%\author{Th\'eo Zimmermann\\
%$\Pi R^2$, Inria and
%IRIF, Paris-Diderot University\\
%Paris, France\\
%Email: theo@irif.fr
%\and
%Annal\'i Casanueva Art\'is\thanks{This work was partly funded by El Conacyt of the Mexican government.}\\
%Paris School of Economics\\
%Paris, France}
%
\maketitle
%
\begin{abstract}
For most software projects, the bug tracker is an essential tool. In open source development, this tool plays an even more central role as it is generally open to all users, who are encouraged to test the software and report bugs. Previous studies have highlighted the act of reporting a bug as a first step leading a user to become an active contributor.

@@

In this paper, we study the case of the Coq proof assistant, a medium-sized open source software project. We use the switch, from Bugzilla to GitHub, of the project's bug tracker, to analyze how a change in the bug reporting environment affects the number of bugs, reporters, bug comments and commentators. Using a temporal Regression on Discontinuity design (RDD)~\cite{angrist2008mostly,angrist2014mastering,jacob2012practical,lee2010regression,hausman2018regression}, we find strong evidence that the change of platform increased the number of bug reports and comments by developers, and increased the number of distinct commentators each week among non-developers. Our results suggest that switching from Bugzilla to GitHub made the bug reporting process easier and more appealing but also opened the software development to more external contributors and stimulated discussion around bugs (notably between developers and non-developers).

@@

The rest of this paper is organized as follows: In Sec.~\ref{related-work}, we discuss related work. In Sec.~\ref{context}, we present the Coq project and the context of the switch. In Sec.~\ref{research_questions}, we present our research questions. In Sec.~\ref{migration}, we explain the migration process. In Sec.~\ref{data}, we describe the data collection and pre-processing method, and we list the variables of interest. In Sec.~\ref{descriptive-stats}, we give a preliminary view of the bug tracking activity. In Sec.~\ref{methodology}, we explain the Regression on Discontinuity methodology, of which we present the results in Sec.~\ref{results}. We interpret the results and relate them to our hypotheses in Sec.~\ref{discussion}. We discuss the threats to validity and  present robustness checks in Sec.~\ref{threats}. We conclude in Sec.~\ref{conclusion}.

@@

From 2007 to 2017, the Coq bug tracker platform was a self-hosted Bugzilla instance (before this, from 2001 to 2007 it was using JitterBug, a now discontinued bug tracking system, and before 2001 a simple mailing list). In 2017, in a context where all code changes were conducted through GitHub pull requests, the question of switching to GitHub's integrated bug tracker arose.
After some preliminary testing showing that migrating all preexisting issues was doable, the Coq development team decided to switch to GitHub issues on October 4th, 2017.

According to the developers we interviewed, the motivations for switching were:
\begin{itemize}
\item Consolidating the development tools on a single, integrated, platform: browsing between code, pull requests and bug reports is easier without having to switch websites. Furthermore, it means a common notification, mention, and assignment system.
\item GitHub's support for formatting and editing comments, cross-referencing and auto-closing issues, and more generally a more pleasant tool to use. On the other hand, many Coq developers perceived Bugzilla as unpleasant, old-fashioned, and very slow. It was a complex tool with many underused advanced features.
\item No need to administrate (maintain and update) the bug tracker. The previous system was perceived as failing often by several developers.
\item Easier to get started for newcomers (especially as many may already know GitHub and already have a GitHub account).
\end{itemize}

Again, according to the developers we interviewed, the principal risks associated with the switch of bug tracker were:
\begin{itemize}
\item Losing control of a critical tool to a private company and its future decisions. In particular, GitHub is not an open source platform (so cannot be cloned elsewhere) and backing up data from GitHub becomes even more important but not trivial to do.
\item Losing or corrupting bug tracking data during the transition from Bugzilla to GitHub. Even if, as we will see in Sec.~\ref{migration}, most of the data was correctly migrated, some meta-data had to be converted to text, and external links and documentation about the bug tracker could have become stale or inaccurate. %In practice, developers were quite happy about the result of the migration.
\item A few developers additionally mentioned risks of losing useful features from Bugzilla, or discouraging developers for whom it would be hard to adapt to the new tool.
\end{itemize}

\section{Research questions}
After a consideration of the motivations and keeping the possible risks in mind, we found particularly interesting and compelling to study the following research questions more in detail to give insights into the effect of a bug tracker switch
\label{research_questions}
%ambre: I think this section should be expanded a bit to add motivation for the hypotheses

%Given the advantages of the GitHub issue tracker that were listed above, one could expect the switch to:
%\begin{description}
%\item[H1] Increase the bug tracking activity, in terms of the number of reported bugs;
%\item[H2] Extend the pool of bug reporters and commentators;
%\item[H3] Increase the bug tracking activity, in terms of the amount of interaction between users and developers.
%\end{description}

\paragraph{RQ1: Impact on level of bug tracking activity.}
%Do not forget the "why"

\paragraph{RQ2: Impact on quality of bug tracking activity.}
\paragraph{RQ3: Impact on the audience of the bug tracker.}

@@

All the data for this study was extracted on January 17\textsuperscript{th}, 2019 using the GitHub GraphQL API \cite{github_graphql_API}. Using this API allows to do large requests (100 nodes in a single request) with just the information we need (thus both reducing the bandwidth usage and speeding up the extraction process). In the supplementary materials, we provide the extracted data as CSV files and a Jupyter notebook with the code to request this data from GitHub, to load the CSV files, to run the pre-processing steps, and the analyses.%, and the robustness checks.

@@

\paragraph{Excluding specific reporters}
We have one specific reporter who is alone responsible for almost a quarter of all bug reports. To avoid having the behavior of a single individual strongly impact the overall statistics, we exclude his comments, bug reports and the comments they received from our analysis. Similarly, we also exclude the developer who was the main advocate of the bug tracker switch as it could have influenced his behavior before and after the switch.

@@

Figures~\ref{bug_nb_with_releases}, \ref{comments_with_releases}, \ref{reporters_with_releases} and \ref{commentators_with_releases} show the evolution of our four main outcome variables since January 2016 until March 2019. We choose to present the data starting in 2016 because on January 2016 the 8.5 version of Coq was released, and this marks the adoption of a more rapid release cycle (with a new major release every 6 to 10 months)\footnote{See \url{https://coq.inria.fr/distrib/V8.9.0/refman/credits.html}.}. This change in the development process could have impacted the activity on the bug tracker and made it not comparable. In Fig.~\ref{bug_nb_with_releases} and \ref{comments_with_releases}, each point represents the 4-week average of the number of issues and number of comments per day respectively for both developers and non-developers. In Fig.~\ref{reporters_with_releases} and \ref{commentators_with_releases}, each point represents the 4-week average of the number of distinct reporters and distinct commentators per week. In all four figures, the vertical red line shows the date of the bug tracker switch; the vertical black lines represent the date of major releases and the discontinuous horizontal lines represent the mean before and after the switch respectively.

Considering the whole period (2016-2019), less issues are reported by developers than by non-developers. In a four-day period, on average, two issues will be opened by developers and five by non-developers (Fig.~\ref{bug_nb_with_releases}). On the contrary, developers post more comments than non-developers. On an average day, developers will post around five comments and non-developers two (Fig.~\ref{comments_with_releases}). This is not surprising because some bugs found by developers are resolved directly without opening an issue and because issue reports are generally answered by developers.
There are more distinct non-developers than developers who open issues in an average week (around six distinct non-developers and two distinct developers, Fig.~\ref{reporters_with_releases}). There are slightly more distinct non-developers (per week) that comment than developers. More precisely, on an average week, around six distinct non-developers and around 5.5 developers comment an issue (Fig.~\ref{commentators_with_releases}).

%It is important to note that we are close to the theoretical saturation of the possible number of distinct developer commentators (already all distinct developers are commenting on weekly basis).
For all outcomes, the mean before the switch is statistically significantly lower than the mean after the switch both for developers and non developers. For some outcomes, the difference in activity patterns before and after the switch is clear to the naked eye. In Fig.~\ref{bug_nb_with_releases} we see an increase in the number of issues reported by developers. In Fig.~\ref{comments_with_releases} we see an increase in the number of comments by developers with several data points after the release that are well above the highest point before the release. Finally, in Fig.~\ref{commentators_with_releases} we see a clear increase in the number of distinct non-developer commentators with the great majority of points after the switch above the great majority of points before the switch. Some other differences may be appreciated but are less clear to the naked eye than those presented.

%The companion Jupyter notebook contains an extensive array of descriptive tables and figures, such as the distribution of bug reporting in the year and in the day, graphs of bug reporting for individual developers, etc. We only present a subset of these results.

@@

%\subsection{Influence of new releases}
%\label{influence_release}

%\paragraph{Influence on the number of bug reports}
%We expect release dates to be correlated to peaks of activity on the bug tracker, in particular peaks of new bug reports. Indeed, users will generally test new releases, for instance by trying to port preexisting projects to the new version, which might lead them to find new bugs (either regressions or bugs related to new features). In Fig.~\ref{bug_nb_with_releases}, we can see that while release dates are generally correlated to peaks of new bug reports by non-developers, this is not so much the case of reports by developers. We can also notice that beta releases are often correlated to higher peaks than final releases which is not surprising given that the users who test beta versions are more likely to be ready to report bugs, and beta versions are likely to be less polished.

%The highest peak is in 2015, after the first beta release of version 8.5. This was the first release in more than two years and it contained five big new features (``the result of five specific long-term projects''\footnote{Quote from:\\ \url{https://coq.inria.fr/distrib/V8.9.0/refman/credits.html\#credits-version-8-5}\\
%The next quotes are coming from the following sections of the same chapter of the Coq reference manual.}). Stabilizing these features and their (unplanned) interactions required more than a year of testing and three beta releases. The 8.5 release was both hard on developers, who found the release cycle too long, and on users, who were impacted by many compatibility issues. Consequently, a different approach was taken for the following releases: versions 8.6, 8.7 and 8.8 were ``developed on a time-based development cycle'' and contain ``the result of refinements, stabilization of features and cleanups of the internals of the system along with a few new features''. Attention was given to regression testing: changes were systematically tested by building a selection of the largest Coq projects. Therefore, it is not surprising that these frequent releases are correlated to smaller peaks of new bug reports.

%IMPORTANT: metre une phrase dans la partie description des variables qui indique qu'on fait 4 semaines pour celui la.
\begin{figure}
\includegraphics{bug_nb_with_releases.eps}
\caption{Number of issues per day (averaged by 4-week periods) with release dates (since 2016).} \label{bug_nb_with_releases}
\end{figure}

%\paragraph{Influence on the number of comments}
%In Fig.~\ref{comments_with_releases}, we can see that release dates are correlated to peaks of comments by developers (and not so much by other people). This is explained by the fact that bug reports are generally answered by developers, thus any peak in bug reporting is bound to induce a peak in bug commenting by developers.

\begin{figure}
\includegraphics{comments_with_releases.eps}
\caption{Number of comments per day (averaged by 4-week periods) with release dates (since 2016).} \label{comments_with_releases}
\end{figure}

\begin{figure}
\includegraphics{reporters_with_releases.eps}
\caption{Number of weekly distinct reporters (averaged by 4-week periods) with release dates (since 2016).} \label{reporters_with_releases}
\end{figure}

\begin{figure}
\includegraphics{commentators_with_releases.eps}
\caption{Number of weekly distinct commentators (averaged by 4-week periods) with release dates (since 2016).} \label{commentators_with_releases}
\end{figure}

@@

\subsection{Quantitative}
We exploit the fact that the switch from Bugzilla to GitHub can be seen as a clear cutoff in time to use a temporal sharp Regression in Discontinuity design (RDD) to estimate the effects of the switch on our outcome variables; to determine if these estimated effects are statistically significant; and to interpret these effects in a causal way. 
The idea behind RDD is that factors that influence bug reporting activity are fairly similar just before and just after the cut-off point, which makes the changes observed between just after and just before the cut-off a consequence of the change that occurred at the cut-off (i.e., the switch of bug reporting platform).

@@

\subsection{Qualitative}

In order to obtain qualitative insights into the effects of the switch that will help us put in context and interpret the quantitative results, we conducted semi-structured interviews of all developers of Coq that were active at the time of the switch (with the exception of the developer that conducted the migration). A total of 9 interviews were conducted between 19th March and 4th April 2019. Some were done face to face and the others by video-conference with an average length of 33.5 minutes per interview. Both authors were present during the interviews and all the interviews were recorded. Some basic questions were asked to all of the interviewees and according to the answers some additional questions were also asked. The answers were coded by both authors in an attempt to minimize errors. Code and questions can be found in the supplementary material.

@@

\begin{table}
\centering
\caption{Estimated impact of the switch on the number of issues. Coefficients are highlighted if they are statistically significant with $p<0.1$ ($\dagger$), $p<0.05$ (*), $p<0.01$ (**) or $p<0.001$ (***). Standard error is in parentheses.}
\label{tab:bug_nb}
\input{bug_nb_rd.tex}
\end{table}

\begin{figure}
\includegraphics{bug_nb_rd.png}
\caption{Number of issues per day before and after the migration (with fitting lines and confidence intervals from the regression results, and points corresponding to average values over two-week periods).} \label{bug_nb_rd}
\end{figure}

@@

\begin{figure}
\includegraphics{reporter_nb_rd.png}
\caption{Number of weekly distinct reporters before and after the migration (with fitting lines and confidence intervals from the regression results, and points corresponding to average values over two-week periods).} \label{reporter_nb_rd}
\end{figure}

@@

\begin{figure}
\includegraphics{comment_nb_rd.png}
\caption{Number of comments per day before and after the migration (with fitting lines and confidence intervals from the regression results, and points corresponding to average values over two-week periods).} \label{comment_nb_rd}
\end{figure}

@@

\begin{figure}
\includegraphics{commentator_nb_rd.png}
\caption{Number of weekly distinct commentators before and after the switch (with fitting lines and confidence intervals from the regression results, and points corresponding to average values over two-week periods).} \label{commentator_nb_rd}
\end{figure}

@@

The biggest concern that we have in our analysis is the fact that the date of the switch is close to the release date of a new version of Coq. The release of version 8.7.0 took place on October 17\textsuperscript{th}, and the migration on October 18\textsuperscript{th}. Then, the hypothesis that there is no other discontinuity around the threshold of interest does not completely hold in our case.
%First, we can argue that only our result on the number of comments by developers is threatened: the other statistically significant effects that we observed are not threatened because there is usually no peak in the corresponding variables after new releases.
%Second, we can also argue that there should have been a similar (or higher) peak in the month before the switch since the first beta of 8.7 had been released then (and beta releases generally result in higher peaks).
To confirm that it is not the migration that is driving our results, we do the exact same analysis that we do for the bug tracker switch, replacing the cutoff date by the date of all six major releases since 2009 (once we remove the latest release because we do not have yet enough data points after the release). We show that the only significant effect in the bug-tracker activity after a major release is the effect after the major release that match the switch. It is also, for the majority of the outcomes, by far the effect with the highest magnitude.

%To provide some evidence that the date of the switch is not associated with an increase in the activity of open source software due to external factors (which will invalidate our results as explained before), we replicate our analysis for a comparable software: another French medium size open-source project: OCaml. We do not observe any increase in the bug-tracking activity for this project after the Coq bug-tracker switch date. If anything we see a decrease in activity so if there was an external factor that affected french open-source projects decreasing their activity. we will be underestimating the effect of the switch.

%two robustness checks with our data. The first consists in removing the two weeks following the 8.7.0 release (and the switch) from our Regressions in Discontinuity. With these periods removed, the regressions still give very close results. The second consists in including a binary control variable that is equal to one if the period is in the two weeks after a release and zero otherwise. This control variable will capture the high peaks due to the release without the need of eliminating periods close to the switch. Again, our results remain very similar when we include this control variable.

@@

Temporal RDD have some notable differences with other types of RDD \cite{hausman2018regression}. One major difference is the capacity of anticipation and reaction to the treatment that affect directly the outcome. To overcome this potential problem, we redo our analysis with a donut RD (i.e. we exclude the data points just after and just before the migration, which are potentially problematic), following \cite{hausman2018regression}. Our results still hold with a slight decrease in the level of significativity but keeping the significativity at 10\%.

@@

%We also conduct one standard robustness check for Regression in Discontinuity analysis by changing the time window of the analysis to fifteen and to ten periods before and after the switch. Our main results are robust to these changes.
All results presented in this section can be found in the Jupyter notebook provided as a supplemental material. 
\subsection{External validity}

@@

% Takeaways
% When to switch? It would be useful to come up with measures that indicate when a bug tracker is not adapted and a switch to another platform would be an improvement. (Or depending on specific objectives.)

\scriptsize
%\paragraph{}
\noindent \footnotesize{\textbf{Supporting data.}}
We provide our extraction and analysis code as a Jupyter notebook and the data we used as CSV files. We also provide the XML export of Bugzilla that was used for the migration and the migration script.
% XXXXX We also provide the interview questions and coding.
%Everything is available from \url{XXXXXXX}.
%\paragraph{}

@@

%\noindent\footnotesize{\textbf{Acknowledgements.}}
%We would like to thank Ambre Williams for valuable advice and help on the design and implementation of the data analyses and C\'ecile Rottner for general advice, support, and proof-reading.
%We would like to thank Andriy Berestovskyy for providing the Bugzilla import tool, and Martin Michlmayr for doing the first steps in porting our modifications upstream.
